\gettitle

### 2019-11-15 assignment2/submission2.tex
Add algorithm for solving 2.2e

\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[a4paper, left=2.5cm, right=2.5cm, top=2.5cm, bottom=4cm]{geometry}
\usepackage[ngerman]{babel}
\usepackage{amsmath, amsthm, amssymb, amstext}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xparse}
\usepackage{fancyhdr}
\usepackage{algorithmicx}
\usepackage{parskip}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{enumerate}
\usepackage{enumitem}
%\usepackage{minted}
\usepackage {tikz}
\usetikzlibrary {positioning}

@@

\subsection*{e)}
\subsection*{f)}

>>>>

\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[a4paper, left=2.5cm, right=2.5cm, top=2.5cm, bottom=4cm]{geometry}
\usepackage[ngerman]{babel}
\usepackage{amsmath, amsthm, amssymb, amstext}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xparse}
\usepackage{fancyhdr}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{parskip}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{enumerate}
\usepackage{enumitem}
%\usepackage{minted}
\usepackage {tikz}
\usetikzlibrary {positioning}

@@

\subsection*{e)}

This code updates the FT entries of \textit{p} for the former successor's predecessor which has the id \textit{q}.

\begin{algorithm}
\begin{algorithmic}
	\For{$i \gets 0 \textbf{ to } \lfloor log_2(q - p) \rfloor$}
	   \State $FT_p[i] \gets q$
	\EndFor
\end{algorithmic}
\end{algorithm}

This code assumes that only \textit{q} has been inserted between \textit{p} and the former successor.
The obvious issue arising from that (namely that multiple insertions are not correctly handled), can be easily remedied by repeating the consistency check after updating the finger table.
As presented the code is already eventually consistent, though.

\subsection*{f)}
